The ChEMBL database as Linked Open Data

### 2013-03-26 article.tex
reference the Open Definition as the definition for open ontologies
the vast majority of so called "open ontologies", including OBO and
Gene Ontology, fail this definition by either restricting use to
academics, and/or restricting modification
of ontologies without onerous conditions like renaming everything

We present here the updated ChEMBL-RDF, including a description of the mapping process 
and the identification of links to other datasets. Because the primary purpose of of this
paper is to expose the ChEMBL data as linked data, less focus has been placed on ontologically
capturing the fine details of the pharmacological literature. This is the reason why
many concepts are not mapped to existing ontologies, though also the lack of ontologies
with a clear open license restrict the options.

>>>>

We present here the updated ChEMBL-RDF, including a description of the mapping process 
and the identification of links to other datasets. Because the primary purpose of of this
paper is to expose the ChEMBL data as linked data, less focus has been placed on ontologically
capturing the fine details of the pharmacological literature. This is the reason why
many concepts are not mapped to existing ontologies, though also the lack of ontologies
with a clear open license, as defined by the Open Definition~\cite{OpenDefinition}, restrict the options.
